---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: "Mecanismos de formación de ensambles de hormigas dentro del ciclo forestal del eucalipto en la Pampa Mesopotámica: el rol de los procesos determinísticos y los factores abióticos"
author:
  - name: '**Pamela E. Pairo**'
    affil: 1
    main: true
    orcid: '0000-0002-8900-896X'
    twitter: pamepairo 
    email: pamepairo@gmail.com
  - name: Carolina Pinto
    affil: 1
    main: true
    email: 'ag.con@posterdown.net'
  - name: M. Isabel Bellocq
    affil: 1
affiliation:
  - num: 1
    address: Laboratorio de Ecología de Comunidades y Macroecología, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Argentina.
output: 
  posterdown::posterdown_html:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
primary_colour: "#3CB371"
titlebox_borderwidth: "0.7cm"
title_textsize: "70pt"
logoleft_name: "figures/uba.png"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introducción

El filtrado ambiental es reconocido como el principal mecanismo formador de ensambles en hábitats antrópicos, aunque poco se sabe acerca del rol de otros procesos determinísticos. 

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectivos

Determinar la acción de los procesos determinísticos en la formación de ensambles de hormigas epígeas en una cronosecuencia forestal e identificar asociaciones entre los rasgos funcionales y las variables ambientales.

# Métodos

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

# Resultados

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# Conclusiones 


# References
